\section{Course program}
The course is structured into eight lectures.
The eight lectures take place during the eight weeks of the course, but are not necessarily in a one-to-one correspondance with the course weeks.

\subsection*{Unit 1}
\paragraph*{Topics}
\begin{itemize}[noitemsep]
	\item Stateful vs stateless computation
  \item Lambda calculus semantics.
    \begin{itemize}[noitemsep]
      \item Variables
      \item Lambda-abstractions/functions
      \item Function application
    \end{itemize}	
  \item Introduction to Typescript
  \item example of lambda calculus in Typescript
  \item Bindings and their semantics in lambda-calculus.
  \item Functional \texttt{if-then-else} and differences with its imperative counterpart.
\end{itemize}

\subsection*{Unit 2}
\paragraph*{Topics}			
\begin{itemize}[noitemsep]
	\item Typed lambda calculus. Typing variables, lambda abstractions, function applications.
  \item Lists and recursion.
  \item Examples on lists.
\end{itemize}

\subsection*{Unit 3}
\paragraph*{Topics}			
\begin{itemize}[noitemsep]
	\item Pipe operator, function composition, map, fold, map2, fold2.
  \item Tuples in lambda calculus and Typescript
  \item Curry and Uncurry
  \item Case Study: SQL
\end{itemize}

\subsection*{Unit 4}
\paragraph*{Topics}			
\begin{itemize}[noitemsep]
	\item Discriminated unions in lambda calculus.
  \item Discriminate unions and records in Typescript.
  \item Pattern matching
  \item Recursive data structures (Trees, Lists with Cons and Empty, …)
  \item Case Study: Expression evaluation  
\end{itemize}

\subsection*{Unit 5}
\paragraph*{Topics}
\begin{itemize}[noitemsep]
  \item List with Cons, Empty. Map and fold with this definition.
  \item Immutable Binary Search Tree. Find, Add, Remove.
  \item String of a tree on console recursive.
  \item Compare two trees.
  \item Graph, DFS, BFS.
  \item Type Classes with function records. 
\end{itemize}
